Simulation Tables

### 2019-06-30 manuscript/manuscript.tex
section 3

A primary goal of the Nurture study is to identify clusters of infants characterized by distinct motor development trajectories. To address this aim, we propose a flexible finite mixture model that accommodates relevant features of the data, such as skewness and dependence among the responses. For $i = 1,...,n$, let $\mathbf{y}_{i}=(y_{i1},\ldots,y_{iJ})^T$ be a $J \times 1$ vector of responses (i.e., Baley scores) for subject $i$ across the $J$ measurement occasions. For the analysis of the Nurture data, we propose a finite mixture model of the form
\begin{equation}
f(\mathbf{y}_i) = \sum_{k = 1}^{K} \pi_{ki} f(\mathbf{y}_i|\boldsymbol\theta_k),
\end{equation}
where $\boldsymbol\theta_k$ is the set of parameters specific to cluster $k$ ($k = 1,...,K$) and $\pi_{ik}$ is a subject-specific mixing weight representing the probability that subject $i$ belongs to cluster $k$. A distinguishing feature of our model is that we treat $\pi_{ik}$ as a gating function (\textbf{cite book}) that depends on a subject's observed data as well as the parameters specific to the cluster to which they belong. For now we assume that $K$ is fixed; in Section 4, we discuss model selection strategies for choosing the optimal value of $K$.

To facilitate posterior inference, we introduce a latent cluster indicator variable $z_i$ taking the value $k \in \{1,...,K\}$ with probability $\pi_{ik}$. Conditional on $z_i = k$, we assume $\mathbf{y}_{i}$ is distributed as
\begin{equation}
\mathbf{y}_{i}|(z_i=k) \sim \text{MSN}_J(\boldsymbol\zeta_{ki},\boldsymbol\alpha_k,\boldsymbol\Omega_k), \label{eq:msndens}
\end{equation}
where $\text{MSN}_J(\cdot)$ denotes the $J$-dimensional multivariate skew normal density, $\boldsymbol\zeta_{ki}$ is a $J \times 1$ vector of subject- and cluster-specific location parameters, $\boldsymbol\alpha_k$ is a $J \times 1$ vector of cluster-specific skewness parameters, and $\boldsymbol\Omega_k$ is a $J \times J$ cluster-specific scale matrix that captures dependence among the $J$ responses for subject $i$. The vector $\boldsymbol\alpha_k$ has components $\alpha_{kj}$, $j = 1,...,J$, that control the skewness of outcome $j$ in cluster $k$. When $\boldsymbol\alpha_k = \mathbf{0}$, the MSN distribution reduces to the multivariate normal distribution $\text{N}_J(\boldsymbol\zeta_k,\boldsymbol\Omega_k)$, where $\boldsymbol\zeta_k$ is a $J \times 1$ mean vector and $\boldsymbol\Omega_k$ is a $J \times J$ covariance matrix (Azzalini and Dalla Valle, 1996).

@@

\subsection{Multinomial Regression for the Cluster Indicators}
To accommodate heterogeneity in the cluster-membership probabilities, we model $\pi_{ik}$ as a function of covariates using a multinomial logit model 
\begin{eqnarray}
\pi_{ik} = \Pr(z_i = k|\mathbf{w}_i) = \frac{\text{e}^{\mathbf{w}_i^T \boldsymbol\delta_k}}{\sum_{h = 1}^K \text{e}^{\mathbf{w}_i^T \boldsymbol\delta_{h}}},~ k=1,\ldots,K,
\end{eqnarray}
where $\mathbf{w}_i$ is an $r\times 1$ vector of subject-level covariates, $\boldsymbol\delta_k$ is a $r\times 1$ vector of regression parameters associated with membership in cluster $k$. For identifiability purposes, we fix the reference category $k = K$ and set $\boldsymbol\delta_K = \mathbf{0}$. Under this model, $z_i|\mathbf{w}_i \sim \text{Multinom}(1,\boldsymbol\pi_i)$, where $\boldsymbol\pi_i = (\pi_{i1},...,\pi_{1K})$. During MCMC estimation, the cluster labels $z_i$ are updated from their multinomial full conditional distribution and used in the remaining MCMC steps as cluster assignments as detailed later in section (\textbf{what section}).

To facilitate sampling, we adopt an efficient data-augmentation approach introduced by Polson \textit{et al.} (2013), which expresses the inverse-logit function as a mixture P\'olya--Gamma densities. By using P\'olya--Gamma data augmentation for the multinomial model (\textbf{cite}), we obtain a P\'olya--Gamma mixture of experts model, a computationally efficient way to model edge weights (\textbf{cite}). A random variable $\mathcal{w}$ is said to follow a P\'olya--Gamma distribution with parameters $b > 0$ and $c \in {\rm I\!R}$ if
\begin{equation}
\mathcal{w} \sim \text{PG}(b,c) \stackrel{d}{=} \frac{1}{2\pi^2}\sum_{s=1}^{\infty}\frac{g_s}{(s-1/2)^2 + c^2/(4\pi^2)}, \label{eq:pg1}
\end{equation}
where $g_s \stackrel{iid}{\sim} \text{Ga}(b,1)$ for $s = 1,...,\infty$ . Polson \textit{et al.} (2013) establish that for the $\text{PG}(b,c)$ density, and for $a,\eta \in {\rm I\!R}$,

\begin{equation}
\frac{(\text{e}^{\eta})^a}{(1 + \text{e}^{\eta})^b} = 2^{-b}\text{e}^{\kappa \eta} \int_{0}^{\infty} \text{e}^{-\mathcal{w}\eta^2/2}p(\mathcal{w}|b,c = 0)d\mathcal{w}. \label{eq:pg2}
\end{equation}
where $\kappa = a - b/2$. Polson \textit{et al.} also show that the conditional distribution $p(\mathcal{w}|b,c)$ results from an ``exponential tilting'' of the $\text{PG}(b,0)$ density, thus

\begin{equation}
	p(\mathcal{w}|b,c) = \frac{\text{e}^{-c^2\mathcal{w}/2}p(\mathcal{w}|b,0)}{E_{\mathcal{w}}[\text{e}^{-c^2\mathcal{w}/2}]} = \frac{\text{e}^{-c^2\mathcal{w}/2}p(\mathcal{w}|b,0)}{\int_0^\infty \text{e}^{-c^2\mathcal{w}/2}p(\mathcal{w}|b,0)d\mathcal{w}}. \label{eq:pg3}
\end{equation}

@@

We can use the quantities to re-express the full conditionals for $\boldsymbol\delta_k$ as
\begin{eqnarray}
	p(\boldsymbol\delta_k|\mathbf{Z},\boldsymbol\delta_{h \ne k}) &\propto& p(\boldsymbol\delta_k) \prod_{i = 1}^{n} \left (\frac{\text{e}^{\eta_{ik}}}{1 + \text{e}^{\eta_{ik}}} \right )^{U_{ik}} \left (\frac{1}{1 + \text{e}^{\eta_{ik}}} \right )^{1-U_{ik}} \nonumber\\ &=& p(\boldsymbol\delta_k) \prod_{i = 1}^n \frac{(\text{e}^{\eta_{ik}})^{U_{ik}}}{1 + \text{e}^{\eta_{ik}}} \label{eq:pglogit}
\end{eqnarray}
which we note is essentially a logistic regression likelihood. We thus apply this P\'olya--Gamma data augmentation scheme from Polson et al. (2013) to update each $\boldsymbol\delta_k$ ($k = 1,...,K-1$) one at a time based on the binary indicators $U_{ik}$.

@@

@@

For cluster $k$, we can collect all observations $\mathbf{y}_i$ ($i = 1,...,n_k$) into the $n_k \times 4$ matrix $\mathbf{Y}_k$ and all covariates $\mathbf{X}_i$ into the $4n_k \times 8$ matrix $\mathbf{X}_k$ (\textbf{clash of notation here}) to utilize the matrix Normal model specification detailed in Section 3, which allows for simultaneous updates of all MSN regression parameters in cluster $k$. For the multinomial regression model component of this simulation, we model the class labels $z_i$ as a function of an intercept and one baseline covariate, thus $r = 2$.

@@

\begin{table}[t]

\caption{\label{tab:unnamed-chunk-4}Model results for simulated data with n = 1500, k = 4, p = 1, h = 3, v = 1. 5000 iterations were run with a burn in of 1000. Missingness mechanism was MAR and P(miss) = 0}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}{llllllll}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{2}{c}{Class 1} & \multicolumn{2}{c}{Class 2} & \multicolumn{2}{c}{Class 3} \\
\cmidrule(l{3pt}r{3pt}){3-4} \cmidrule(l{3pt}r{3pt}){5-6} \cmidrule(l{3pt}r{3pt}){7-8}
Model Component & Parameter & True & Est. (95\% CrI) & True & Est. (95\% CrI) & True & Est. (95\% CrI)\\
\midrule
\addlinespace[0.3em]
\multicolumn{8}{l}{\textbf{ }}\\
\hspace{1em}MVSN & $\beta_{0}$ & -3.21 & -3.34 (-3.8, -2.99) & -0.32 & -0.33 (-0.48, -0.14) & 3.35 & 3.33 (3.22, 3.44)\\
\hspace{1em}Regression & $\beta_{1}$ & -3.08 & -3.3 (-3.73, -2.87) & -0.75 & -0.72 (-0.87, -0.52) & 2.6 & 2.5 (2.39, 2.6)\\
\hspace{1em} & $\beta_{2}$ & -2.97 & -3.18 (-3.58, -2.76) & -0.45 & -0.44 (-0.58, -0.26) & 3.43 & 3.42 (3.31, 3.53)\\
\hspace{1em} & $\beta_{3}$ & -2.91 & -3.08 (-3.49, -2.68) & -0.66 & -0.68 (-0.83, -0.48) & 3.04 & 2.98 (2.87, 3.09)\\
\addlinespace[0.3em]
\multicolumn{8}{l}{\textbf{ }}\\
\hspace{1em} & $\sigma_{11}$ & 1 & 0.95 (0.84, 1.02) & 1 & 1 (0.89, 1.11) & 1 & 1.06 (0.97, 1.16)\\
\hspace{1em} & $\sigma_{12}$ & 0.74 & 0.7 (0.59, 0.76) & 0.68 & 0.68 (0.59, 0.78) & -0.45 & -0.41 (-0.47, -0.36)\\
\hspace{1em} & $\sigma_{13}$ & 0.74 & 0.69 (0.58, 0.75) & -0.16 & -0.13 (-0.2, -0.06) & 0.82 & 0.88 (0.79, 0.97)\\
\hspace{1em} & $\sigma_{14}$ & 0.98 & 0.93 (0.81, 0.99) & 0.64 & 0.65 (0.56, 0.75) & 0.7 & 0.75 (0.67, 0.83)\\
\hspace{1em} & $\sigma_{22}$ & 1 & 0.94 (0.82, 1.01) & 1 & 1.03 (0.93, 1.13) & 1 & 1.07 (0.99, 1.16)\\
\hspace{1em} & $\sigma_{23}$ & 0.83 & 0.79 (0.67, 0.85) & -0.43 & -0.4 (-0.46, -0.34) & -0.66 & -0.62 (-0.68, -0.57)\\
\hspace{1em} & $\sigma_{24}$ & 0.81 & 0.77 (0.66, 0.83) & 0.63 & 0.67 (0.58, 0.77) & 0.01 & 0.07 (0.01, 0.13)\\
\hspace{1em} & $\sigma_{33}$ & 1 & 0.96 (0.84, 1.03) & 1 & 1 (0.91, 1.09) & 1 & 1.05 (0.96, 1.15)\\
\hspace{1em} & $\sigma_{34}$ & 0.85 & 0.81 (0.69, 0.87) & 0.15 & 0.15 (0.08, 0.23) & 0.59 & 0.64 (0.56, 0.72)\\
\hspace{1em} & $\sigma_{44}$ & 1 & 0.95 (0.83, 1.01) & 1 & 1.02 (0.92, 1.13) & 1 & 1.06 (0.97, 1.15)\\
\addlinespace[0.3em]
\multicolumn{8}{l}{\textbf{ }}\\
\hspace{1em} & $\psi_{1}$ & -0.33 & -0.33 (-0.62, 0.69) & 0.67 & 0.7 (0.46, 0.89) & -1 & -1.01 (-1.13, -0.87)\\
\hspace{1em} & $\psi_{2}$ & -0.33 & -0.32 (-0.61, 0.64) & 0.67 & 0.63 (0.38, 0.82) & -1 & -0.88 (-1.01, -0.75)\\
\hspace{1em} & $\psi_{3}$ & -0.33 & -0.33 (-0.61, 0.69) & 0.67 & 0.64 (0.43, 0.82) & -1 & -1.01 (-1.14, -0.88)\\
\hspace{1em} & $\psi_{4}$ & -0.33 & -0.31 (-0.63, 0.67) & 0.67 & 0.7 (0.45, 0.89) & -1 & -0.94 (-1.07, -0.81)\\
\addlinespace[0.3em]
\multicolumn{8}{l}{\textbf{ }}\\
\hspace{1em}Multinom. & $\delta_{11}$ & 0.9 & 0.88 (0.81, 0.95) & 0.9 & 0.88 (0.81, 0.95) & 0.9 & 0.88 (0.81, 0.95)\\
\hspace{1em} & $\delta_{12}$ & 0.23 & 0.22 (0.14, 0.3) & 0.23 & 0.22 (0.14, 0.3) & 0.23 & 0.22 (0.14, 0.3)\\
\addlinespace[0.3em]
\multicolumn{8}{l}{\textbf{ }}\\
\hspace{1em}Clustering & $\pi_l$ & 0.28 & 0.28 (0.27, 0.28) & 0.42 & 0.43 (0.42, 0.43) & 0.3 & 0.3 (0.3, 0.3)\\
\bottomrule
\end{tabular}
\end{table}

@@

@@

>>>>

A primary goal of the Nurture study is to identify clusters of infants characterized by distinct motor development trajectories. To address this aim, we propose a flexible finite mixture model that accommodates relevant features of the data, such as skewness and dependence among the responses. For $i = 1,...,n$, let $\mathbf{y}_{i}=(y_{i1},\ldots,y_{iJ})^T$ be a $J \times 1$ vector of responses (i.e., Baley scores) for subject $i$ across the $J$ measurement occasions. For the analysis of the Nurture data, we propose a finite mixture model of the form
\begin{equation}
f(\mathbf{y}_i) = \sum_{k = 1}^{K} \pi_{ki} f(\mathbf{y}_i|\boldsymbol\theta_k),
\end{equation}
where $\boldsymbol\theta_k$ is the set of parameters specific to cluster $k$ ($k = 1,...,K$) and $\pi_{ki}$ is a subject-specific mixing weight representing the probability that subject $i$ belongs to cluster $k$. For now we assume that $K$ is fixed; in Section 4, we discuss model selection strategies for choosing the optimal value of $K$.

To facilitate posterior inference, we introduce a latent cluster indicator variable $z_i$ taking the value $k \in \{1,...,K\}$ with probability $\pi_{ik}$. Conditional on $z_i = k$, we assume $\mathbf{y}_{i}$ is distributed as
\begin{equation}
\mathbf{y}_{i}|(z_i=k) \sim \text{MSN}_J(\boldsymbol\zeta_{ki},\boldsymbol\alpha_k,\boldsymbol\Omega_k), \label{eq:msndens}
\end{equation}
where $\text{MSN}_J(\cdot)$ denotes the $J$-dimensional multivariate skew normal density, $\boldsymbol\zeta_{ki}$ is a $J \times 1$ vector of subject- and cluster-specific location parameters, $\boldsymbol\alpha_k$ is a $J \times 1$ vector of cluster-specific skewness parameters, and $\boldsymbol\Omega_k$ is a $J \times J$ cluster-specific scale matrix that captures dependence among the $J$ responses for subject $i$. The vector $\boldsymbol\alpha_k$ has components $\alpha_{kj}$, $j = 1,...,J$, that control the skewness of outcome $j$ in cluster $k$. When $\boldsymbol\alpha_k = \mathbf{0}$, the MSN distribution reduces to the multivariate normal distribution $\text{N}_J(\boldsymbol\zeta_{ki},\boldsymbol\Omega_k)$, where $\boldsymbol\zeta_{ki}$ is a $J \times 1$ mean vector and $\boldsymbol\Omega_k$ is a $J \times J$ covariance matrix (Azzalini and Dalla Valle, 1996).

@@

\subsection{Multinomial Regression for the Cluster Indicators}
To accommodate heterogeneity in the cluster-membership probabilities, we model $\pi_{ik}$ as a function of covariates using a multinomial logit model 
\begin{eqnarray}
\pi_{ik} = \Pr(z_i = k|\mathbf{w}_i) = \frac{\text{e}^{\mathbf{w}_i^T \boldsymbol\delta_k}}{\sum_{h = 1}^K \text{e}^{\mathbf{w}_i^T \boldsymbol\delta_{h}}},~ k=1,\ldots,K,
\end{eqnarray}
where $\mathbf{w}_i$ is an $r\times 1$ vector of subject-level covariates, $\boldsymbol\delta_k$ is a $r\times 1$ vector of regression parameters associated with membership in cluster $k$. For identifiability purposes, we fix the reference category $k = K$ and set $\boldsymbol\delta_K = \mathbf{0}$. Under this model, $z_i|\mathbf{w}_i \sim \text{Multinom}(1,\boldsymbol\pi_i)$, where $\boldsymbol\pi_i = (\pi_{i1},...,\pi_{1K})$. During MCMC estimation, the cluster labels $z_i$ are updated from their multinomial full conditional distribution and used in the remaining MCMC steps as cluster assignments as detailed later in section (\textbf{what section}). By allowing the cluster probabilities to vary across subjects, our model can be viewed as a \textit{mixture of experts} model in which $\pi_{ki}$ acts as a \textit{gating function} (\textbf{cite book}).

To facilitate sampling, we adopt an efficient data-augmentation approach introduced by Polson \textit{et al.} (2013), which expresses the inverse-logit function as a mixture P\'olya--Gamma densities. By using P\'olya--Gamma data augmentation for the multinomial model (\textbf{cite}), we obtain a P\'olya--Gamma mixture of experts model, a computationally efficient way to model edge weights (\textbf{cite}). A random variable ${w}$ is said to follow a P\'olya--Gamma distribution with parameters $b > 0$ and $c \in {\rm I\!R}$ if
\begin{equation}
{w} \sim \text{PG}(b,c) \stackrel{d}{=} \frac{1}{2\pi^2}\sum_{s=1}^{\infty}\frac{g_s}{(s-1/2)^2 + c^2/(4\pi^2)}, \label{eq:pg1}
\end{equation}
where $g_s \stackrel{iid}{\sim} \text{Ga}(b,1)$ for $s = 1,...,\infty$ . Polson \textit{et al.} (2013) establish that for the $\text{PG}(b,c)$ density, and for $a,\eta \in {\rm I\!R}$,

\begin{equation}
\frac{(\text{e}^{\eta})^a}{(1 + \text{e}^{\eta})^b} = 2^{-b}\text{e}^{\kappa \eta} \int_{0}^{\infty} \text{e}^{-{w}\eta^2/2}p({w}|b,c = 0)d{w}. \label{eq:pg2}
\end{equation}
where $\kappa = a - b/2$. Polson \textit{et al.} also show that the conditional distribution $p(w|b,c)$ results from an ``exponential tilting'' of the $\text{PG}(b,0)$ density, thus

\begin{equation}
	p({w}|b,c) = \frac{\text{e}^{-c^2{w}/2}p({w}|b,0)}{E_{{w}}[\text{e}^{-c^2{w}/2}]} = \frac{\text{e}^{-c^2{w}/2}p({w}|b,0)}{\int_0^\infty \text{e}^{-c^2{w}/2}p({w}|b,0)d{w}}. \label{eq:pg3}
\end{equation}

@@

We can use the quantities to re-express the full conditionals for $\boldsymbol\delta_k$ as
\begin{eqnarray}
	p(\boldsymbol\delta_k|\mathbf{U}_k,\boldsymbol\delta_{h \ne k}) &\propto& p(\boldsymbol\delta_k) \prod_{i = 1}^{n} \left (\frac{\text{e}^{\eta_{ik}}}{1 + \text{e}^{\eta_{ik}}} \right )^{U_{ik}} \left (\frac{1}{1 + \text{e}^{\eta_{ik}}} \right )^{1-U_{ik}} \nonumber\\ &=& p(\boldsymbol\delta_k) \prod_{i = 1}^n \frac{(\text{e}^{\eta_{ik}})^{U_{ik}}}{1 + \text{e}^{\eta_{ik}}} \label{eq:pglogit}
\end{eqnarray}
which we note is essentially a logistic regression likelihood. We thus apply this P\'olya--Gamma data augmentation scheme from Polson et al. (2013) to update each $\boldsymbol\delta_k$ ($k = 1,...,K-1$) one at a time based on the binary indicators $U_{ik}$.

@@

We model fit diagnostics, we choose the WAIC statistic introduced by Watanabe (2010). To specify the number of cluster $K$, we follow Neelon and Chung (2016), who use WAIC to determine the optimal number of latent factors in a Bayesian latent factor zero-inflated Poisson model for the analysis of correlated and zero-inflated count data. In Section 6, we discuss possible extentions to other methods for choosing $K$.

@@

For cluster $k$, we can collect all observations $\mathbf{y}_i$ ($i = 1,...,n_k$) into the $n_k \times 4$ matrix $\mathbf{Y}_k$ and all covariates $\mathbf{X}_i$ into the $4n_k \times 8$ matrix $\mathbf{X}_k$ (\textbf{clash of notation here}) to utilize the matrix Normal model specification detailed in Section 3, which allows for simultaneous updates of all MSN regression parameters in cluster $k$. For the multinomial regression model component of this simulation, we model the class labels $z_i$ as a function of an intercept and one baseline covariate, thus $r = 2$. We leave the problem of missing data to simulation study \#2 and do not incorporate missing data into this simulation.

@@

@@

In our second simulation study, we compare our online conditional multivariate normal imputation method to standard Bayesian multiple imputation.

@@

\bibitem{ } Neelon B, Chung D. The LZIP: A Bayesian latent factor model for correlated zero‐inflated counts. Biometrics. 2017 Mar;73(1):185-96.

### 2019-06-30 mcmc_draws_2019-06-27/tables.Rmd
section 3

---
title: "Simulation Tables"
author: "Carter Allen"
date: "4/21/2019"
output: 
  pdf_document: 
    keep_tex: yes
---

@@

```{r}
load("BETA")
load("beta_true")
load("DELTA")
load("delta_true")
load("PI")
load("PSI")
load("psi_true")
load("SIGMA")
load("sig2_true")
load("pi_true")
load("Z")
```

@@

model_component <- c("MVSN","Regression","","","","","","","","","","","","","","","","",
                     "Multinom.","",
                     "Clustering")
params <- c("$\\beta_{0}$","$\\beta_{1}$","$\\beta_{2}$","$\\beta_{3}$",
            "$\\sigma_{11}$","$\\sigma_{12}$","$\\sigma_{13}$","$\\sigma_{14}$",
            "$\\sigma_{22}$","$\\sigma_{23}$","$\\sigma_{24}$",
            "$\\sigma_{33}$","$\\sigma_{34}$",
            "$\\sigma_{44}$",
            "$\\psi_{1}$","$\\psi_{2}$", "$\\psi_{3}$","$\\psi_{4}$",
            "$\\delta_{11}$","$\\delta_{12}$",
            "$\\pi_l$")

@@

```{r}
rownames(t1) <- NULL
kable(t1, booktabs = T, escape = F,caption = "Model results for simulated data with n = 1500, k = 4, p = 1, h = 3, v = 1. 5000 iterations were run with a burn in of 1000. Missingness mechanism was MAR and P(miss) = 0") %>%
  kable_styling(font_size = 8) %>%
  add_header_above(c(" " = 2,"Class 1" = 2, "Class 2" = 2, "Class 3" = 2)) %>%
  group_rows(" ",1,4) %>%
  group_rows(" ",5,14) %>%
  group_rows(" ",15,18) %>%
  group_rows(" ",19,20) %>%
  group_rows(" ",21,21)
```

```{r,eval=FALSE}

kable(t1,booktabs = T,escape = F,caption = "Model results for simulated data with n = 500, k = 4, p = 2, h = 3, v = 3. 500 iterations were run with a burn in of 100. Missingness mechanism was MAR and P(miss) = 0.25.",
      row.names = NA) %>%
    kable_styling(font_size = 8) %>%
    add_header_above(c(" " = 2,"Class 1" = 2, "Class 2" = 2, "Class 3" = 2)) %>%
    group_rows(" ",1,4) %>%
    group_rows(" ",5,7) %>%
    group_rows(" ",8,10) %>%
    group_rows(" ",11,11) %>%
    group_rows(" ",12,12)
```

>>>>

---
title: "Simulation Tables"
author: "Carter Allen"
date: 
output: 
  pdf_document: 
    keep_tex: yes
---

@@

```{r}
setwd("~/Documents/School/Summer_2019/Research/MVSN-FMM/mcmc_draws_2019-06-27")
load("BETA")
load("beta_true")
load("DELTA")
load("delta_true")
load("PI")
load("PSI")
load("psi_true")
load("SIGMA")
load("sig2_true")
load("pi_true")
load("Z")
```

@@

model_component <- c("MVSN","Regression","","","","","","","","","","","","","","","","","","","","",
                     "Multinom.","","","",
                     "Clustering")
params <- c("$\\beta_{11}$","$\\beta_{21}$","$\\beta_{31}$","$\\beta_{41}$",
            "$\\beta_{12}$","$\\beta_{22}$","$\\beta_{32}$","$\\beta_{42}$",
            "$\\sigma_{11}$","$\\sigma_{12}$","$\\sigma_{13}$","$\\sigma_{14}$",
            "$\\sigma_{22}$","$\\sigma_{23}$","$\\sigma_{24}$",
            "$\\sigma_{33}$","$\\sigma_{34}$",
            "$\\sigma_{44}$",
            "$\\psi_{1}$","$\\psi_{2}$", "$\\psi_{3}$","$\\psi_{4}$",
            "$\\delta_{11}$","$\\delta_{12}$",
            "$\\delta_{21}$","$\\delta_{22}$",
            "$\\pi_l$")

@@

```{r}
rownames(t1) <- NULL
kable(t1, booktabs = T, escape = F,caption = "Model results for simulated data with n = 1000, k = 4, p = 2, h = 3, r = 2. 1000 iterations were run with a burn in of 250. Missingness mechanism was MAR and P(miss) = 0") %>%
  kable_styling(font_size = 8) %>%
  add_header_above(c(" " = 2,"Class 1" = 2, "Class 2" = 2, "Class 3" = 2)) %>%
  group_rows(" ",1,8) %>%
  group_rows(" ",9,18) %>%
  group_rows(" ",19,22) %>%
  group_rows(" ",23,26) %>%
  group_rows(" ",27,27)
```
